Efficient Development Framework with mruby\\for Embedded Systems

### 2016-06-07 CPSNA2016/paper.tex
update CPSNA2016

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran/IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

% \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
\title{Efficient Development Framework with mruby \\for Embedded Systems}
\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale such by cyber physical systems.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
In the proposed framework, a Bluetooth loader which receives a transferred mruby bytecode from a host, and a RiteVM scheduler which simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

@@

\section{Introduction}
Currently, embedded systems such as Cyber Physical Systems must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

@@

mruby programs consist of an mruby application and mruby libraries.
An mruby application is the main program code, mruby libraries define the functions for the application, such as Ruby classes. 
The mruby bytecodes including both an mruby application and mruby libraries can be transferred and executed on the target device.
However, this is also wasteful in terms of bytecode size and the time required to transfer the bytecodes, because the libraries are not modified frequently.
With the proposed framework, only mruby applications are transferred, and the mruby libraries are preserved on the storage/ROM device beforehand.
As a result, RiteVMs can share mruby libraries.
In addition, a RiteVM can use its own library, which other RiteVMs should not use.

@@

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{par:hr-tecs}).
The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader.
Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.
The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tRiteVMBluetooth1 {
    entry sTaskBody eMrubyBody;
    [optional] call sEventflag cEventflag[];
    [optional] call sSemaphore cSemaphore;
    attr {
      FLGPTN setPattern;
      [omit]char_t *mrubyLib;
      char_t *irepLib = C_EXP("&$cell_global$_irep");
      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
    };
    var {
        mrb_state *mrb;
        mrbc_context *context;
        [size_is(irepAppSize)] char_t *irepApp;
    };
};
\end{lstlisting}
    \vspace{-3mm}
\caption{Celltype description for RiteVM with Bluetooth loader}
    \vspace{-3mm}
\label{celltype_mrubybluetooth}
\end{figure}

@@

@@

Second, {\it mrb\_state} and {\it mrbc\_context} pointers (Figure \ref{fig:control_flow}(B); lines 7, 9 in Figure \ref{maincode_mrubybluetooth}).
{\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}.
{\it mrb\_state} is a set of states and global variables used in mruby.
The synchronization of multiple tasks is performed in this processing phase.
The RiteVM that finishes execution at this point waits for the another RiteVM to finish loading and initialization.

Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}(C); line 12 in Figure \ref{maincode_mrubybluetooth}).
The mruby libraries are a set of Ruby classes, such as the motor and sensor classes.
For example, the motor class defines methods to rotate and stop a motor.
The tRiteVMBluetooth {\it cell} has the attributes shown in Figure \ref{celltype_mrubybluetooth}.
{\it ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\it VAR}.
The {\it mrubyLib} indicates the program files of the mruby libraries, and is an attribute because mruby libraries are not modified in the proposed development process.
Here, {\it [omit]} is only used for the TECS generator; thus, the attribute {\it mrubyLib} does not consume memory.
{\it irepLib} is the pointer of the array in which the bytecode of mruby libraries is stored.
To summarize, the bytecode of mruby libraries is stored as an attribute of the component during the first compilation.

Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); line 14 in Figure \ref{maincode_mrubybluetooth}).
The mruby application bytecode is stored in an array of {\it irepApp}.
Note that two bytecodes, irepLib and irepApp, are read separately in the RiteVM.

Finally, the mruby task runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
When an mruby application is modified, only the bytecode of the modified application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
% The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
% When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
The proposed framework supports continuous loading; thus, this process loops.
After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.

@@

\subsection{Improving Development Efficiency by Bluetooth Loader}
The Bluetooth loader can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

%\subsubsection{Size and time for transferred mruby bytecodes}
In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
The size, load process time, and compilation time for an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
The overhead of load processing to load a zero byte bytecode is 50.933 msec.
Similarly, compilation overhead to compile a zero byte program is 46.9 msec.
The mruby application bytecode is smaller and faster than including the mruby libraries for all terms.
The difference increases as the number of RiteVMs increases because 50 msec of overhead is incurred per RiteVM. 
These advantages improve the efficiency of software development.

\begin{table}[t]
    \centering
    \vspace{-2mm}
\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
    \vspace{-2mm}
    %\scriptsize
    {\tabcolsep=0.3cm
    \begin{tabular}{l||r|r|c}
                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
          Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
          Compile Time      & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
          \vspace{-3mm}
    \label{tab:size_and_time}
\end{table}

\subsection{RiteVM Scheduler}
A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.

\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
This shows that the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

\subsection{Synchronization of Multiple RiteVM Tasks}
To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
Figure \ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
As shown in Figure \ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.

\subsection{Benefits of Component-Based Development}
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
Developers can add or remove the functionalities easily by modifying the CDL file.
Moreover, CBD decreases code size and improves productivity and maintainability.

%\subsubsection{Code size utilizing component-based development}
To demonstrate the superiority of CBD, a comparison of the number of lines of codes between two C and CDL files is shown in Table \ref{tab:codesize}.
In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Figure \ref{fig:Eventflag}, respectively. 
For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
Note that (B)'s C file can be utilized without modification regardless of the number of RiteVMs.
Moreover, the number of code lines of two CDL files are equal.
Skillful CBD yields advantages such as the decreased number of lines of codes and non-modified codes, which facilitates high productivity and maintainability.

@@

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[h]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
    \vspace{-2mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{-2mm}
    \label{fig:mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \vspace{-2mm}
    \caption{Component Diagram}
    \vspace{-2mm}
    \label{fig:component}
\end{figure}

@@

@@

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[ht]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees, [in] uint32_t speed_abs,\\ [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Signature Description}
    \vspace{-2mm}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[ht]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Celltype Description}
    \vspace{-2mm}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[ht]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Build Description}
    \vspace{-2mm}
\label{build}
\end{figure}

\end{description}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
    \vspace{-2mm}
\caption{System model of existing mruby on TECS}
    \vspace{-2mm}
\label{fig:mrubyontecs}
\end{figure}

>>>>

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran/IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

% \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
\title{Efficient Development Framework with mruby\\for Embedded Systems}
\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems applied to Cyber Physical Systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
In the proposed framework, a Bluetooth loader which receives an mruby bytecode, and a RiteVM scheduler which simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

@@

\section{Introduction}
Cyber Physical Systems (CPS) is the important keyword for enriching our lives.
Embedded systems e.g., Internet of Things applications, are applied to the CPS and expected to demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in the large source code, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

@@

mruby programs consist of an mruby application and mruby libraries.
An mruby application is the main program code, mruby libraries define the functions for the application, such as Ruby classes. 
The mruby bytecodes including both an mruby application and mruby libraries can be transferred and executed on the target device.
However, this is also wasteful in terms of bytecode size and the time required to transfer the bytecodes, because the libraries are not modified frequently.
With the proposed framework, only mruby applications are transferred, and the mruby libraries are preserved on the storage/ROM device beforehand.
% As a result, RiteVMs can share mruby libraries.
% In addition, a RiteVM can use its own library, which other RiteVMs should not use.

@@

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{par:hr-tecs}).
The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader.
Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader, such as RiteVMBluetooth1.
In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.
The main process of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.

@@

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tRiteVMBluetooth1 {
    /* An entry port for tTask */
    entry sTaskBody eMrubyBody;
    /* A call port for Eventflag components */
    [optional] call sEventflag cEventflag[];
    /* A call port for a Semaphore component */
    [optional] call sSemaphore cSemaphore;
    attr {
      [omit]char_t *mrubyLib;
      char_t *irepLib = C_EXP("&$cell_global$_irep");
    };
    var {
      mrb_state *mrb;
      mrbc_context *context;
      [size_is(irepAppSize)] char_t *irepApp;
    };
};
\end{lstlisting}
    \vspace{-3mm}
\caption{Celltype description for RiteVM with Bluetooth loader}
    \vspace{-3mm}
\label{celltype_mrubybluetooth}
\end{figure}

@@

Second, {\it mrb\_state} and {\it mrbc\_context} pointers are initialized (Figure \ref{fig:control_flow}(B); lines 7, 9 in Figure \ref{maincode_mrubybluetooth}).
{\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}, and which are a set of states and global variables used in mruby.
Note that the synchronization of multiple tasks is performed in this processing phase (Section \ref{sec:Synchronization of Multiple RiteVM Tasks}).
% The RiteVM that finishes execution at this point waits for the another RiteVM to finish loading and initialization.

Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}(C); line 12 in Figure \ref{maincode_mrubybluetooth}).
The mruby libraries are a set of Ruby classes, such as the motor and sensor classes.
For example, the motor class defines methods to rotate and stop a motor.
The tRiteVMBluetooth {\it cell} has the attributes shown in Figure \ref{celltype_mrubybluetooth}.
{\it ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\it VAR}.
The {\it mrubyLib} indicates the program files of the mruby libraries, and is an attribute because mruby libraries are not modified in the proposed development process.
Here, {\it [omit]} is only used for the TECS generator; thus, the attribute {\it mrubyLib} does not consume memory.
{\it irepLib} is the pointer of the array in which the bytecode of mruby libraries is stored.
To summarize, the bytecode of mruby libraries is stored as an attribute of the component (i.e., {\it irepLib}) during the first compilation.

Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); line 14 in Figure \ref{maincode_mrubybluetooth}).
The mruby application bytecode is stored in an array of {\it irepApp}.
Here, {\it [size\_is()]} is the specifier for an array.
Note that two bytecodes, {\it irepLib} and {\it irepApp}, are read separately in the RiteVM.

Finally, the RiteVM runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
When an mruby application is modified, only the bytecode of the application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
% The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
% When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
The proposed framework supports continuous loading; thus, this process loops.
After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.
In addition, the proposed framework supports the reset component which force applications stop and free, thus developers can transfer new bytecodes and run tasks.

@@

{\bf Improving Development Efficiency by Bluetooth Loader}:
The Bluetooth loader can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

%\subsubsection{Size and time for transferred mruby bytecodes}
In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
To confirm the advantage of the proposed design, we evaluated the size, loading time, and compile time between an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
Loading Time indicates how long it takes to process a transferred bytecode in the loader, and the overhead of loading a zero byte bytecode is 50.933 msec.
Similarly, the overhead to compile a zero byte program is 46.9 msec.
The mruby application bytecode is smaller and faster than including the mruby libraries for all terms.
The difference increases as the number of RiteVMs increases because 50 msec of overhead is incurred per RiteVM. 
These advantages improve the efficiency of software development.

\begin{table}[t]
    \centering
    \vspace{-2mm}
\caption{Comparison between an application with and without libraries}
    \vspace{-2mm}
    %\scriptsize
    {\tabcolsep=0.3cm
    \begin{tabular}{l||r|r|c}
                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
          Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
          Compile Time      & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
          \vspace{-3mm}
    \label{tab:size_and_time}
\end{table}

{\bf RiteVM Scheduler}:
A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
We decided a program with 100,000 loops as an mruby application for the evaluation of execution time.
Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.

\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletasking, Co-routine, and Proposed Multitasking}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitasking and co-routine.
Therefore, the scheduler enables developers multitasking as the more efficient approach than co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

{\bf Synchronization of Multiple RiteVM Tasks}:
To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
Figure \ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
As shown in Figure \ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.

{\bf Benefits of Component-Based Development}:
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
Developers can add or remove the functionalities easily by modifying the CDL file.
Moreover, CBD decreases code size and improves productivity and maintainability.

%\subsubsection{Code size utilizing component-based development}
To demonstrate the superiority of CBD, a comparison of the number of lines of C and CDL codes between two situations is shown in Table \ref{tab:codesize}.
In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Figure \ref{fig:Eventflag}, respectively. 
For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
Moreover, (B)'s C file can be utilized without modification regardless of the number of RiteVMs, while the number of code lines of two CDL files are equal.
Skillful CBD yields advantages such as the decreased number of lines of codes and non-modified codes, which facilitates high productivity and maintainability.

@@

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[h]
    \centering
    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
    \vspace{-2mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{-2mm}
    \label{fig:mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \vspace{-2mm}
    \caption{Component Diagram}
    \vspace{-5mm}
    \label{fig:component}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{lstlisting}
signature sMotor {
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Signature Description}
    \vspace{-5mm}
\label{signature}
\end{figure}

\begin{figure}[H]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Celltype Description}
    \vspace{-5mm}
\label{celltype}
\end{figure}

\begin{figure}[H]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Build Description}
    \vspace{-2mm}
\label{build}
\end{figure}

@@

% \begin{description}
    %\item[
    {\bf Signature Description:\ }%]\mbox{}\\
        {\it Signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.

    %\item[
    {\bf Celltype Description:\ }%]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.

    %\item[
    {\bf Build Description:\ }%]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
    \vspace{-2mm}
\caption{System model of existing mruby on TECS}
    \vspace{-2mm}
\label{fig:mrubyontecs}
\end{figure}
